---
title: "PIPS_Assignment3.2R.2_Make_art_Function"
output: html_document
date: "2024-01-27"
---

## The make_art function
With the following function you can create random art. You can add an optional 
argument (seed = random number), but as optional implies, this is not necessary.
If you decide to not add a number, the default is seed = 10. 
Now you can start and explore the function!

## The code
This is the code to initiate the make_art function:

```{r}
# install.packages("ggplot2")
library(ggplot2)

make_art <- function(seed = 10) {
  my_art <- ggplot() +
    geom_segment(aes(x = 1:100, xend = seed, y = seq(1, 10, length.out = 100), 
                     yend = seed + 5), colour = "#750052") +
    geom_curve(aes(x = 1:100, xend = seed, y = seq(1, 10, length.out = 100), 
                   yend = seed + 5), colour = "#007680") +
    geom_curve(aes(x = 10:109, xend = seed, y = seq(10, 19, length.out = 100), 
                   yend = seed + 5), colour = "#cfcf60") +
    geom_curve(aes(x = 20:119, xend = seed, y = seq(20, 29, length.out = 100), 
                   yend = seed + 5), colour = "#ff187d") +
    geom_segment(aes(x = -1:-100, xend = seed, y = seq(1, 10, length.out = 100), 
                     yend = seed + 5), colour = "#000000") +
    geom_curve(aes(x = -1:-100, xend = seed, y = seq(1, 10, length.out = 100), 
                   yend = seed + 5), colour = "#ffffff") +
    geom_curve(aes(x = -10:-109, xend = seed, y = seq(10, 19, length.out = 100), 
                   yend = seed + 5), colour = "#ffffff") +
    geom_curve(aes(x = -20:-119, xend = seed, y = seq(20, 29, length.out = 100), 
                   yend = seed + 5), colour = "#000000") +
    geom_segment(aes(x = 1:100, xend = -seed, y = seq(1, 10, length.out = 100), 
                     yend = -seed - 5), colour = "#000000") +
    geom_curve(aes(x = 1:100, xend = -seed, y = seq(1, 10, length.out = 100), 
                   yend = -seed - 5), colour = "#ffffff") +
    geom_curve(aes(x = 10:109, xend = -seed, y = seq(10, 19, length.out = 100), 
                   yend = -seed - 5), colour = "#ffffff") +
    geom_curve(aes(x = 20:119, xend = -seed, y = seq(20, 29, length.out = 100), 
                   yend = -seed - 5), colour = "#000000") +
    geom_segment(aes(x = -1:-100, xend = -seed, y = seq(1, 10, length.out = 100), 
                     yend = -seed - 5), colour = "#750052") +
    geom_curve(aes(x = -1:-100, xend = -seed, y = seq(1, 10, length.out = 100), 
                   yend = -seed - 5), colour = "#007680") +
    geom_curve(aes(x = -10:-109, xend = -seed, y = seq(10, 19, length.out = 100), 
                   yend = -seed - 5), colour = "#cfcf60") +
    geom_curve(aes(x = -20:-119, xend = -seed, y = seq(20, 29, length.out = 100), 
                   yend = -seed - 5), colour = "#ff187d") +
    theme_void()
  return(my_art)
}
```

## The output
This is some output with the default (seed = 10):

```{r}
make_art()
```

This is some output with a higher argument value, (seed = 50):

```{r}
make_art(seed = 50)
```

This is some output with a lower argument value, (seed = -50):

```{r}
make_art(seed = -50)
```

